Understanding the impacts of video-guided activities on parent-child interaction

### 2020-08-26 paper/manuscript_anonymized.tex
added research highlights, video transcripts

\PassOptionsToPackage{unicode=true}{hyperref} % options for packages loaded elsewhere
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provides euro and other symbols
\else % if luatex or xelatex
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage[]{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\usepackage{hyperref}
\hypersetup{
            pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
            pdfauthor={George Kachergis, Emily Hembacher, Veronica Cristiano, Hanwen Vivian Zhang, \& Michael C. Frank},
            pdfkeywords={digital parenting advice; joint attention; lexical diversity; guided play},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

% set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother

\shorttitle{Impacts of videos on parent-child interaction}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Department of Psychology, Stanford University\\\textsuperscript{2} Gallaudet University\\\textsuperscript{3} Cornell University}
\keywords{digital parenting advice; joint attention; lexical diversity; guided play\newline\indent Word count: 4995}
\usepackage{csquotes}
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

\usepackage{longtable}
\usepackage{lscape}
\usepackage{multirow}
\usepackage{tabularx}
\usepackage[flushleft]{threeparttable}
\usepackage{threeparttablex}

\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

\usepackage{lineno}

\linenumbers
\usepackage{float}

\title{Understanding the impacts of video-guided activities on parent-child interaction}
\author{George Kachergis\textsuperscript{1}, Emily Hembacher\textsuperscript{1}, Veronica Cristiano\textsuperscript{2}, Hanwen Vivian Zhang\textsuperscript{3}, \& Michael C. Frank\textsuperscript{1}}
\date{}

@@

Correspondence concerning this article should be addressed to Michael C. Frank, Stanford, CA 94305 USA. E-mail: \href{mailto:mcfrank@stanford.edu}{\nolinkurl{mcfrank@stanford.edu}}}

\abstract{
Early parenting practices play an important role in shaping the future outcomes of young children (Hart \& Risley, 1995; Heckman, 2006).
In particular, high-quality early interactions and language input appear to facilitate language learning and result in higher levels of school performance.
The rise of phone-based parenting applications (``apps'') holds the promise of delivering low-cost, positive interventions on parenting style to a wide variety of populations.
Of special interest are the parents of very young children, who are often difficult to reach in other ways. Yet little is known about the effects of communicating to parents through app-based interventions.
We showed parents short videos depicting age-appropriate parent-child activities from a commercial parenting app, and found that the quality of parent-child interactions increased in some ways as a result of the intervention.
Specifically, after watching the activity video, parents spoke more and made more bids for joint attention with the child.

@@

@@

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting the Children's Discovery Museum in San Jose to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

\hypertarget{participants.}{%
\subsubsection{Participants.}\label{participants.}}

60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in northern California.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

\hypertarget{materials.}{%
\subsubsection{Materials.}\label{materials.}}

@@

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (see SI).

\hypertarget{procedure.}{%
\subsubsection{Procedure.}\label{procedure.}}

@@

\hypertarget{joint-attention-coding-procedure.}{%
\subsubsection{Joint Attention Coding Procedure.}\label{joint-attention-coding-procedure.}}

@@

Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski et al. (2019a)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; Makowski et al., 2019b; McElreath, 2018). Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.24, 89\% CI = {[}-14.07, -4.21{]}, \emph{pd} = 1), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens (\(\beta=\) 16.50, 89\% CI = {[}5.78, 27.2{]}, \emph{pd} = 0.99), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf. int.): {[}60, 79{]}) than in the No Video condition (mean: 52, 95\% conf. int.: {[}44, 61{]}).

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Parents' bid rate was greater in the Activity Video condition (mean: 3, sd: 1.11) than in the No Video condition (mean: 2.15, sd: 1.02, \(\beta=0.72\), 89\% CI = {[}0.12, 1.32{]}, \emph{pd} = 0.97).
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.81\), 89\% CI = {[}0.87, 13.13{]}, \emph{pd} = 0.97).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.34\), 89\% CI = {[}-0.62, -0.07{]}, \emph{pd} = 0.98).
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.23, 1.03{]}, \emph{pd} = 0.99).
Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.45, -0.04{]}, \emph{pd} = 0.97).
Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.82\), 89\% CI = {[}0.06, 1.54{]}, \emph{pd} = 0.96).

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (see SI for the interactive corpus characteristic plot).
Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words tokens per minute to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: \href{https://osf.io/2bpdf}{https://osf.io/2bpdf/}.}

@@

\hypertarget{participants.-1}{%
\subsubsection{Participants.}\label{participants.-1}}

@@

\hypertarget{materials.-1}{%
\subsubsection{Materials.}\label{materials.-1}}

@@

\hypertarget{procedure.-1}{%
\subsubsection{Procedure.}\label{procedure.-1}}

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.05{]}, \emph{pd} = 1).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table 1.

\begin{table}[tbp]
\begin{center}
\begin{threeparttable}
\caption{\label{tab:e2tab}Mean lexical diversity measures in Experiment 2.}
\begin{tabular}{lllllllll}
\toprule
Condition & \multicolumn{1}{c}{TTR} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{MTLD} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Types} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Tokens} & \multicolumn{1}{c}{(sd)}\\
\midrule
Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
\bottomrule
\end{tabular}
\end{threeparttable}
\end{center}
\end{table}

@@

This work was supported by a gift and a contract from Kinedu, Inc.~to the Language and Cognition Lab.
Thanks to Samaher Radwan and Megan Merrick for behavioral coding of the videos, and to members of the Language and Cognition Lab at Stanford for helpful discussion.

@@

\leavevmode\hypertarget{ref-Breitenstein2016}{}%
Breitenstein, S. M., Fogg, L., Ocampo, E. V., Acosta, D. I., \& Gross, D. (2016). Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial. \emph{JMIR mHealth and uHealth}, \emph{4}(2), e36. \url{http://doi.org/10.2196/mhealth.5202}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Understanding the impacts of video-guided activities on parent-child interaction},
  pdfauthor={XXXX1, XXXX1, XXXX2, XXXX3, \& XXXX1},
  pdflang={en-EN},
  pdfkeywords={language development; parent intervention; childhood development; joint attention; lexical diversity},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\patchcmd{\HyOrg@maketitle}
  {\section{\protect\normalfont{\@title}}}
  {\section*{\protect\normalfont{\@title}}}
  {}{\typeout{Failed to patch title.}}
\makeatother
\shorttitle{Impacts of videos on parent-child interaction}
\keywords{language development; parent intervention; childhood development; joint attention; lexical diversity\newline\indent Word count: 5066}
\DeclareDelayedFloatFlavor{ThreePartTable}{table}
\DeclareDelayedFloatFlavor{lltable}{table}
\DeclareDelayedFloatFlavor*{longtable}{table}
\makeatletter
\renewcommand{\efloat@iwrite}[1]{\immediate\expandafter\protected@write\csname efloat@post#1\endcsname{}}
\makeatother
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\usepackage{float}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi

\title{Understanding the impacts of video-guided activities on parent-child interaction}
\author{XXXX\textsuperscript{1}, XXXX\textsuperscript{1}, XXXX\textsuperscript{2}, XXXX\textsuperscript{3}, \& XXXX\textsuperscript{1}}
\date{}

@@

The data that support the findings of this study are openly available in OSF at {[}XXXX{]}

Correspondence concerning this article should be addressed to XXXX, XXXX. E-mail: XXXX

@@

\affiliation{\vspace{0.5cm}\textsuperscript{1} XXXX\\\textsuperscript{2} XXXX\\\textsuperscript{3} XXXX}

\abstract{
Early parenting practices play an important role in shaping children's future outcomes.
In particular, high-quality early interactions can facilitate language learning and school performance.
The rise of phone-based parenting applications (``apps'') could deliver low-cost interventions on parenting style to a wide variety of populations, especially the parents of very young children, who are often difficult to reach in other ways.
Yet little is known about the effects of communicating to parents through app-based interventions.
In two studies (one preregistered), we showed parents short videos depicting age-appropriate parent-child activities from a parenting app.
We found that after watching the video, parents spoke more and made more bids for joint attention, as compared with controls who watched no video (experiment 1) or a science video (experiment 2).
These results suggest that activity videos can lead to positive changes in parent engagement, providing support for the use of such videos in parenting interventions.
}

@@

\hypertarget{research-highlights}{%
\section{Research Highlights}\label{research-highlights}}

\begin{itemize}
\tightlist
\item
  After watching short activity videos in a parenting app, parents made more attempts to engage with their children and spoke more to them.
\item
  Older toddlers showed greater engagement after parents watched the activity videos, relative to younger toddlers.
\item
  These activity videos led parents to set more goals for their child during play.
\item
  Our findings suggest that parent-led activities guided by apps may be helpful in scaffolding the play of older toddlers.
\end{itemize}

@@

In Experiment 1, we invited parents of 6- to 24-month-old infants visiting a children's museum in XXXX to complete video-guided activities from a commerical parenting app that delivers digital parenting advice in the form of short videos.
Parents were randomly assigned to one of two conditions: parents in the \emph{Activity Video} condition watched a video from the app (matched to their child's age), and then performed the activity with their child using the props from the video.
Parents in the \emph{No Video} condition did not watch an activity video, but were given a set of the same age-appropriate props and asked to play with their infants as they normally would at home.

@@

\hypertarget{participants}{%
\subsubsection{Participants}\label{participants}}

60 infants (F = 43, M = 17) aged 6-24 months (19 6-11.9 month-olds: 9 in the control condition, 10 in Activity Video; 20 12-17.9 month-olds: 11 control, 9 Activity Video; 21 18-24 month-olds: 10 control, 11 Activity Video) and their parents participated in a museum in XXXX.
We included infants who were exposed to English at least 50 percent of the time (n = 58) or who were exposed less but whose participating parent reported that they primarily speak English with their child at home (n = 2).
62\% of participants (n = 37) had been exposed to two or more languages, as indicated by their parent.
Parents identified their children as White (n = 25), Asian (n = 11), African American/Black (n = 2), Biracial (n = 12), other (n = 5), or declined to state (n = 5).
Fifteen parents reported that their child was of Hispanic origin.
Parents tended to be highly-educated, with reports of highest level of education ranging from completed high school (n = 5), some college (n = 7), four-year college (n = 16), some graduate school (n = 2), to completed graduate school (n = 30).

\hypertarget{materials}{%
\subsubsection{Materials}\label{materials}}

@@

Participants were randomly assigned to either the \emph{Activity Video} condition or the \emph{No Video} condition.
Parents participating in the Activity Video condition were assigned to watch one of the two activity videos available for their child's age group, while parents in the No Video condition watched no video, and were simply asked to play with their child as they normally would.
The two conditions were yoked: for each Activity Video participant who saw a particular video and received the associated props, a participant in the No Video condition received the same props to use without seeing the video.
Parents also completed the Early Parenting Attitudes Questionnaire (EPAQ; Hembacher \& Frank, 2020).
The EPAQ measures parents of young children's attitudes about parenting and child development along three dimensions: rules and respect, early learning, and affection and attachment (\href{XXX}{see SI}).

\hypertarget{procedure}{%
\subsubsection{Procedure}\label{procedure}}

@@

\hypertarget{joint-attention-coding-procedure}{%
\subsubsection{Joint Attention Coding Procedure}\label{joint-attention-coding-procedure}}

@@

Parents' child-directed speech during the play sessions (mean duration: 3.25 min) was transcribed; child utterances were not considered.
Although Experiment 1 was not preregistered, for consistency the transcripts and hand-coded joint attention data were analyzed according to our preregistration for Experiment 2\footnote{Preregistration: {[}XXX{]}}, with any deviations or exploratory analyses noted.
Below we first report the lexical diversity results, followed by the joint attention results.

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of condition, age (centered), and their interaction with a random intercept per video using rstanarm (Goodrich, Gabry, Ali, \& Brilleman, 2018).
For effects that are at least 95\% likely to be non-zero according to the posterior distribution (i.e., probability of direction: \emph{pd}; Makowski et al. (2019a)), we report estimated coefficients (\(\beta\)) as well as 89\% Bayesian credible intervals (89\% CI)\footnote{89\% CIs are recommended for Bayesian analyses because unless the effective sample size (ESS) is on the order of 10,000, the 95\% credible interval is unstable (Kruschke, 2014; Makowski et al., 2019b; McElreath, 2018). Our ESS ranges from 2,000-5,000, and thus we report the tighter, more stable interval.}, demarcating the range within which 89\% of the posterior falls, meaning that given the observed data, the effect has 89\% probability of falling within this range (see Appendix for more an illustrated explanation).
There was lower TTR in the Activity Video condition (mean: 0.32) than in the No Video condition (mean: 0.43, \(\beta=\)-0.11, 89\% CI = {[}-0.15, -0.07{]}, \emph{pd} = 1).
A similar regression instead predicting MTLD also found lower lexical diversity in the Activity Video condition (mean MTLD: 17.87) than in the No Video condition (mean: 27.09, \(\beta=\)-9.25, 89\% CI = {[}-14.25, -4.16{]}, \emph{pd} = 1), with no notable influence of age.
Figure \ref{fig:lexdiv} (top) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.

We also conducted similar regressions predicting the rate of word tokens and types per minute of play, finding a notable effect of condition on the rate of word tokens (\(\beta=\) 16.56, 89\% CI = {[}6.38, 27.27{]}, \emph{pd} = 0.99), with parents using tokens at a higher rate in the Activity Video condition (mean: 69 tokens/min, bootstrapped 95\% confidence interval (conf. int.): {[}60, 79{]}) than in the No Video condition (mean: 52, 95\% conf. int.: {[}44, 61{]}).

@@

We fit a Bayesian mixed-effects linear regression predicting the rate of parent bids (per minute) for joint attention (JA) as a function of fixed effects of condition, age (centered), and their interaction, with random intercepts per video.
Parents' bid rate was greater in the Activity Video condition (mean: 3, sd: 1.11) than in the No Video condition (mean: 2.15, sd: 1.02, \(\beta=0.72\), 89\% CI = {[}0.14, 1.32{]}, \emph{pd} = 0.98).
Mixed-effects regressions with the same structure were performed predicting the rate of episodes of coordinated and passive JA, and the time spent in coordinated and passive JA.
There were no notable effects on the rate of episodes nor on the time spent in coordinated or passive JA episodes.
Figure \ref{fig:JA} (top) shows the mean rate of bids and episodes of JA by condition in Experiment 1.

@@

We also fit Bayesian mixed-effects linear regression models predicting each of the above lexical diversity and joint attention dependent variables as a function of fixed effects of condition, age (centered), the child's sex, parent's education level, and the subscales of the EPAQ: Early Learning (EL), Affection and Attachment (AA), and Rules and Respect (RR), along with interactions of condition and EL, AA, and RR.
These models included random intercepts per video.
Of these exploratory regressions, two showed notable effects involving the EPAQ subscales, and one other showed an effect of the child's sex.
First, in the word types regression, parents with higher Affection and Attachment scores used more word types per minute after watching an Activity Video (interaction of condition and AA: \(\beta=6.85\), 89\% CI = {[}0.74, 12.91{]}, \emph{pd} = 0.96).
Second, in the regression examining the rate of passive JA episodes, parents scoring higher on the Rules and Respect (RR) subscale had a lower rate of passive JA episodes (\(\beta=-0.35\), 89\% CI = {[}-0.63, -0.06{]}, \emph{pd} = 0.97).
However, after an Activity Video, higher RR parents did not show this decrease in passive JA (interaction of condition and RR: \(\beta=0.63\), 89\% CI = {[}0.22, 1.03{]}, \emph{pd} = 0.99).
Parents with higher education also showed a lower rate of passive JA episodes (\(\beta=-0.25\), 89\% CI = {[}-0.46, -0.05{]}, \emph{pd} = 0.97).
Finally, parents with male children made bids for JA at a higher rate (mean: 2.76 bids/min) than those with female children (mean: 2.49, \(\beta=0.81\), 89\% CI = {[}0.07, 1.57{]}, \emph{pd} = 0.96).

To get a better sense of the intervention's effect on language use, we analyzed which words were characteristic of parents' speech in each condition, comparing the difference in frequency rank of each word (lemma) in the two conditions, as well as contrasting the corpus overall with a general English-language word frequency list (\href{https://cogsciguy.github.io/parenting_obs_language/Exp1_characteristic_chart.html}{see SI}
for the interactive corpus characteristic plot).
Words that were strongly indicative of being from the Activity Video condition include \enquote{give}, \enquote{big}, \enquote{small}, \enquote{ribbit}, \enquote{thank}, \enquote{have}, and \enquote{bus}, while words that were most characteristic of the No Video condition include \enquote{shake}, \enquote{ready}, \enquote{oh}, \enquote{on}, \enquote{going}, \enquote{going}, \enquote{see}, \enquote{let}, and the child's name.

@@

Experiment 1 found that parents who watched an activity video made more bids for joint attention and spoke more words tokens per minute to their children, but had lower lexical diversity compared to parents who played with their children as they normally would at home.
Might it be that parents who are focused on a specific activity show reduced lexical diversity due to their focus on engaging their child in the activity?
Experiment 2 focuses on replicating the key findings using a stronger control group, as well as a restricted number of preregistered predictions.\footnote{Preregistration: {[}XXX{]}}

@@

\hypertarget{participants-1}{%
\subsubsection{Participants}\label{participants-1}}

@@

\hypertarget{materials-1}{%
\subsubsection{Materials}\label{materials-1}}

@@

\hypertarget{procedure-1}{%
\subsubsection{Procedure}\label{procedure-1}}

@@

We fit a Bayesian mixed-effects linear regression predicting TTR as a function of age (centered) and condition with an interaction term, and with random intercepts per video.
This revealed lower TTR after the Activity Video (mean: 0.38) than after the Science Video (mean: 0.48, \(\beta=-0.09\), , 89\% CI = {[}-0.14, -0.04{]}, \emph{pd} = 1).
The preregistered regression predicting the number of tokens used by parents revealed no effects.
An exploratory mixed-effects linear regression predicting MTLD found no effect of age or condition.
Figure \ref{fig:lexdiv} (bottom left and middle) shows the mean of each lexical diversity measure (TTR and MTLD) by condition.
Regressions with the same structure predicting the number of words tokens found no effect of age or condition.
The means of the lexical measures are shown in Table 1.

\begin{table}[tbp]

\begin{center}
\begin{threeparttable}

\caption{\label{tab:e2tab}Mean lexical diversity measures in Experiment 2.}

\begin{tabular}{lllllllll}
\toprule
Condition & \multicolumn{1}{c}{TTR} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{MTLD} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Types} & \multicolumn{1}{c}{(sd)} & \multicolumn{1}{c}{Tokens} & \multicolumn{1}{c}{(sd)}\\
\midrule
Science Video & 0.48 & 0.08 & 22.45 & 10.57 & 28.05 & 8.54 & 61.85 & 23.58\\
Activity Video & 0.38 & 0.12 & 20.63 & 8.66 & 26.57 & 8.39 & 77.22 & 32.09\\
\bottomrule
\end{tabular}

\end{threeparttable}
\end{center}

\end{table}

@@

XXXX

@@

\leavevmode\hypertarget{ref-Breitenstein2016}{}%
Breitenstein, S. M., Fogg, L., Ocampo, E. V., Acosta, D. I., \& Gross, D. (2016). Parent use and efficacy of a self-administered, tablet-based parent training intervention: A randomized controlled trial. \emph{JMIR mHealth and uHealth}, \emph{4}(2), e36. \url{https://doi.org/10.2196/mhealth.5202}
